---
title: "munqc (Munsell Quality Control) package for R"
output_format: gfm
knitr:
    opts_chunk:
        collapse: true
        comment: "#>"
        fig.align: "center"
        retina: 1.5
        messaage: false
        warning: false
        tidy: false

---

The idea behind the munqc package was developed to help determine when the 
UNL soil judging team should consider replacing their Munsell Soil Color books.
Since the experiment showed interesting results and plots, munqc was developed
so that other users of Munsell Soil Color books could see how their books were
standing the test of time.

## Installation

The stable version is not yet available on CRAN...

Development version:

```r
remotes::install_github("asub-sandwich/munqc", build = FALSE)
```

## Examples

### Summary of scans and decisions
```{r example_summary}
library(munqc)

# example data (the 22 original UNL soil judging team book scans)
data(example_scans)

# subset the data to only include books 1 and 2
x <- subset_ids(example_scans, c("book_1", "book_2"))

# compute the errors of the scanned books
x <- compute_error(x)

# print a summary assessment of your books
summary(x)
```

### Scan plotting
```{r example_plot, fig.width = 9, fig.height = 16, fig.alt='im a readme example', fig.caption='im a readme example'}
library(munqc)

# example data (the 22 original UNL soil judging team book scans)
data(example_scans)

# subset the data to only include books 1 and 2
x <- subset_ids(example_scans, c("book_1", "book_2"))

# compute the errors of the scanned books
x <- compute_error(x, thresholds = munqc_thresholds(fail_at = 2))

# plotting the measured colors on a 'page-space' plot, with empirically-determined
# tolerance windows
plot(x, type = "page_space")
```

## Citation
```{r}
citation("munqc")
```

## Related Papers
* Hopefully coming soon!

## Related Presentations
* Also hopefully coming soon!